Wired for Success: Sweden's Electrical Innovators in the Age of Industrial Transformation

### 2023-10-31 index.qmd
add data

>>>>

## How to get a text embedding?

# Define a function to get the text embedding
def get_embedding(text, model="text-embedding-ada-002"):
    text = text.replace("\n", " ")
    return openai.Embedding.create(input=[text], model=model)['data'][0]['embedding']

# Apply the get_embedding function to your 'hisco_text' column
df['ada_embedding'] = df['hisco_text'].apply(lambda x: get_embedding(x, model='text-embedding-ada-002'))
